Hydras \& Co.

### 2022-01-31 doc/gaia-chapter.tex
add more snippets
add stuff in gaia-chapter

\section{Porting theorems without big effort}

\subsection{Porting a theorem from \gaia}
The \texttt{Gaia} library contains a proof that the multiplication of ordinals less than $\epsilon_0$ is associative.

\emph{From~\href{https://github.com/coq-community/gaia/blob/master/theories/ssete9.v}{gaia.ssete9.v}}

@@

@@

\begin{todo}
Explain the proof !
\end{todo}

\inputsnippets{GCanon/gcanonLimitOf}

>>>>

\subsection{Porting a theorem from \gaia}
The \texttt{Gaia} library already contains a proof that the multiplication of ordinals less than $\epsilon_0$ is associative.
\emph{From~\href{https://github.com/coq-community/gaia/blob/master/theories/ssete9.v}{gaia.ssete9.v}}

@@

Many lemmas of the library \texttt{ordinals/Epsilon0/} are statements about inhabitants of type \texttt{hT1}. In order to get
similar statements on \gaia's type \texttt{T1}, we prove and
apply rewriting rules of the following forms:

\vspace{4pt}

\noindent\emph{From Module~\href{../theories/html/gaia.T1Bridge.html}{gaia.T1Bridge}}

\inputsnippets{T1Bridge/T1leIff}
\inputsnippets{T1Bridge/rewritingRules}
\inputsnippets{T1Bridge/limitbRef}

Please note that in this module, we favour \gaia's notations over hydra's. A snippet like \texttt{alpha < succ beta} should be interpreted as \texttt{T1lt alpha beta}, where \texttt{T1lt} is defined in \texttt{gaia.ssete9.v}. The corresponding statement is
written \texttt{hlt (g2h alpha) (g2h beta)}.

@@

The following lemmas are proved by rewriting from corresponding statements proved in \Hydras.

\inputsnippets{GCanon/g2hCanonRw}
\inputsnippets{GCanon/gcanonLt}
\inputsnippets{GCanon/glimitCanonSNotZero}
\inputsnippets{GCanon/gcanonLimitV2}
\inputsnippets{GCanon/gcanonLimitMono}
\inputsnippets{GCanon/gcanonLimitOf}
